R Markdown Features

### 2018-07-11 GitHubPage/my_R_book/Rmarkdown_features/rmd_features.rmd
up

---
title: "R Markdown Features"
subtitle: "A Compact Reference"
author: "[Yongfu Liao](https://liao961120.github.io/)"
date: "`r Sys.Date()`"
bibliography: /home/liao/local_depend/citation/neanderthals.bib
csl: /home/liao/local_depend/style_sheets/apa.csl
link-citations: yes
output:
  bookdown::html_document2:
    code_folding: show
    css: /home/liao/local_depend/style_sheets/style.css
    df_print: kable
    toc: true
    toc_depth: 2
    toc_float:
        collapsed: false
---

@@

- Prefix & Suffix
    - `Some text [see @Bib.ID1 pp.45; also, @Bib.ID2 ch. 2].`
    -  Some text [see @RN9 pp. 45; also, @RN15 ch. 2].

@@

<iframe src="https://www.slideshare.net/slideshow/embed_code/key/1xBpPrD61JbE0w" width="550" height="500" frameborder="0" marginwidth="0" marginheight="0" scrolling="no" style="border:0px solid #FFFFFF; border-width:0px; margin-bottom:5px; max-width: 100%;" allowfullscreen></iframe>

[Download](https://github.com/liao961120/local_depend/blob/master/GitHubPage/my_R_book/Rmarkdown_features/beamer/beamer.pdf)

>>>>

---
title: "R Markdown Features"
subtitle: "A Compact Reference"
author: "[Yongfu Liao](https://liao961120.github.io/)"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
bibliography: /home/liao/local_depend/citation/neanderthals.bib
csl: /home/liao/local_depend/style_sheets/apa.csl
link-citations: yes
output:
  bookdown::html_document2:
    code_folding: show
    css: /home/liao/local_depend/style_sheets/style.css
    df_print: kable
    toc: true
    toc_depth: 2
    toc_float:
        collapsed: false
---

@@

- Prefix & Suffix
    - `Text [see @Bib.ID1 pp.45; also, @Bib.ID2 ch. 2].`
    -  Text [see @RN9 pp. 45; also, @RN15 ch. 2].

@@

<iframe src="https://www.slideshare.net/slideshow/embed_code/key/1xBpPrD61JbE0w" width=90%" height="440" frameborder="0" marginwidth="0" marginheight="0" scrolling="no" style="border:0px solid #FFFFFF; border-width:0px; margin-bottom:0px; max-width: 100%;" allowfullscreen></iframe>

Note: In full screen mode (on PC), you can use arrow keys to navigate through the slides.

[Download Beamer Slide](https://github.com/liao961120/local_depend/blob/master/GitHubPage/my_R_book/Rmarkdown_features/beamer/beamer.pdf)
